---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DepCens

<!-- badges: start -->
<!-- badges: end -->

The package *DepCens* uses dependent censoring regression models for survival multivariate data. These models are based on extensions of the frailty models, capable to accommodating the dependence between failure and censoring times, with Weibull and piecewise exponential marginal distributions.

## Installation

The latest stable version can be installed from CRAN:

```{r, eval=FALSE}
install.packages('DepCens')
```

The latest development version can be installed from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
#install.packages("devtools")
devtools::install_github('GabrielGrandemagne/DepCens')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DepCens)
#KidneyMimic is our simulated data frame
delta_t <- ifelse(KidneyMimic$cens==1,1,0)
delta_c <- ifelse(KidneyMimic$cens==2,1,0)
fit <- dependent.censoring(formula = time ~ x1 + x2 | x3 + x1, data=KidneyMimic, delta_t=delta_t,
                           delta_c=delta_c, ident=KidneyMimic$ident, dist = "weibull")
summary_dc(fit)
```

*KidneyMimic* is our simulated data frame. For more information check the documentation for stored datasets.

```{r}
head(KidneyMimic)
```

You can also plot the survival function

```{r plot_dc}
plot_dc(fit, scenario = "t")
```
